### 2017-03-27 paper/frag_implementation.tex
More progress

\begin{listing}
+-----------------------------------+
| ver(1) | op(1)  | reserved (2)    |
+-----------------------------------+
|           rip (4 bytes)           |
+-----------------------------------+
| rpt (2 bytes)   | dpt (2 bytes)   |
+-----------------|-----------------+
\end{listing}

>>>>

\begin{lstlisting}
+-----------------------------------+
| ver(1) | op(1)  | reserved (2)    |
+-----------------------------------+
|           rip (4 bytes)           |
+-----------------------------------+
| rpt (2 bytes)   | dpt (2 bytes)   |
+-----------------|-----------------+
\end{lstlisting}

The \texttt{ver} field is a protocol version, currently set to 1. The
\texttt{op} field contains the operation of this message: request (0) or
response (1). The \texttt{reserved} field is unused, currently existing to pad
the request. The field \texttt{rip} (short for ``remote IP'') is the address
that the client wishes to create a detour to. \texttt{rpt} is the TCP port on
the server to create a detour to. To understand the \texttt{dpt} field, it is
useful to describe all of the addresses and ports in use during a tunneled
connection:
\begin{itemize}
\item Client IP, port: the IP address of the client, and the client-side port,
  which is usually ephemeral.
\item Detour IP, port (client side): the IP and port that the client will
  address its communication to.
\item Detour IP, port (remote side): the IP and port which are used when the
  detour opens its corresponding connection on the remote.
\item Remote IP, port: the IP and port which the client is tunneling its
  connection to.
\end{itemize}

The \texttt{dpt} field corresponds to the detour port, client side. In a
request, the client proposes a port. In the response, the detour specifies the
actual port which will be used. The server may wish to alter the \texttt{dpt}
field for several reasons:
\begin{itemize}
\item A tunnel to the remote IP, port pair is already open on a different detour
  port.
\item The client already has a detour open (to a different remote) on the given
  port.
\item The detour may have a socket accepting connection on the proposed port,
  and so it may wish to avoid creating a tunnel which would prevent the client
  from accessing that service.
\end{itemize}

In order to create the tunnels, the detour runs two IPTables commands, which
create NAT rules.
